---
title: "Bryan Crenshaw's 52 Weekly Saunter Challenge"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Inspired by the [52 Hike Challenge](https://www.52hikechallenge.com/), I am taking my own approach, by going on a weekly "saunter" on a different local trail for every week of 2020. These hikes will be summarized in a table below with links to the route on tracking software sites, in case you are interested in taking your own saunter along those trails. If you are curious about why I use the term saunter, instead of hike, it comes from a quote by John Muir, who also preferred the term saunter (see the [*About* page](about.html) for details).  

---

## Hikes Thus Far ##


| Date    | Park                  | Trail  |
|---------|-----------------------|-------------|
|1-Jan-20| Marsh Creek State Park	|[White Trail](https://www.alltrails.com/explore/recording/marsh-creek-trail--382)|
|5-Jan-20| Wissahickon	          |Carpenter's Woods Trails|
|11-Jan-20|Wissahickon	          |Towanda>White>Lavender|
|12-Jan-20|Delaware Water Gap	    |[Mt Minsi via AT](https://www.alltrails.com/explore/recording/mount-minsi-via-appalachian-trail--1464)|
|15-Jan-20|Wissahickon	          |Kitchens Lane>White>Orange|
|19-Jan-20|	Hopewell FurnaceNHS/French Creek State Park	|[Lenape Trail to Mill Creek Trail Loop](https://www.alltrails.com/explore/recording/lenape-trail-to-mill-creek-trail-loop--69)|
|26-Jan-20|	Hickory Run SP	      |[Shades of Death](https://www.alltrails.com/explore/recording/shades-of-death-trail--588)|
|03-Feb-20|	Hickory Run SP	      |[Skyline>Fireline from Hickory Run](https://www.alltrails.com/explore/recording/skyline-trail--5929)|
|08-Feb-20|	Nolde Forest SP       |[Nolde Forest Trail](https://www.alltrails.com/explore/recording/nolde-forest-trail--412)|

```{r}

```

