---
title: "Bryan Crenshaw's 52 Saunters Challenge 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)
```


Inspired by the [52 Hike Challenge](https://www.52hikechallenge.com/), I am taking my own approach, by going on a "saunter" on a different trail averaging one for every week of 2020. These hikes will be summarized in a table below with links to the route on tracking software sites, in case you are interested in taking your own saunter along those trails. If you are curious about why I use the term saunter, instead of hike, it comes from a quote by John Muir, who also preferred the term saunter (see the [*About* page](about.html) for details).  

---

## Outings Log ##

```{r LoadLibraries}
library(openxlsx)
suppressPackageStartupMessages(library(dplyr))
library(tidyr)
library(knitr)
library(stringr)
library(kableExtra)

```

```{r Functions}

# blank_href <- function()
```


```{r Input Data}

hikes  <-  read.xlsx('data/52-Hike-Challenge-Hiking-Log_2020.xlsx', startRow = 6) 
names(hikes) <- c('hike_num', 'date', 'park_area', 'trail', 'distance', 'time', 'elevation_gain', 'difficulty', 'recording_app', 'recording_html')

hikes <- 
  hikes %>% 
  mutate(date = convertToDate(date)) %>% 
  drop_na(date, park_area, trail)

# Prepare df for output
hikes_out <- 
  hikes %>% 
  mutate(date = format(date, "%d-%b-%y")) %>% 
  mutate(Trail = cell_spec(trail, "html", link = recording_html)) %>%
  rename(Date = date, Park = park_area) %>%
  select(Date, Park, Trail)  %>% 
  mutate(Trail = ifelse(str_detect(Trail, 'href="NA"'), 
                            str_extract(Trail, "(?<=\\>).+(?=\\<)"), 
                            Trail)
         )
# ^^^ In the final mutate above, the cell_spec() generates a link with no target
# Therefore, the blank links (e.g. href="NA") were converted to just the name - no link to nowhere. 

# Output to table
knitr::kable(hikes_out, caption = NULL, escape = FALSE) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),
                              # full_width = FALSE,
                              position = "left")
```


