---
title: "Bryan Crenshaw's 52 Weekly Saunter Challenge"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Inspired by the [52 Hike Challenge](https://www.52hikechallenge.com/), I am taking my own approach, by taking a weekly "saunter" in a different local trail for every week of 2020. These hikes will be summarized in a table on the home page with links to tracking software sites, so that folks can take their own saunters (If you are curious about the name, see the [*About* page](about.html)).  

---

## Hikes Thus Far ##


| Date    | Park                  | Trail  |
|---------|-----------------------|-------------|
|1-Jan-20| Marsh Creek State Park	|[White Trail](https://www.alltrails.com/explore/recording/marsh-creek-trail--382)|
|5-Jan-20| Wissahickon	          |Carpenter's Woods Trails|
|11-Jan-20|Wissahickon	          |Towanda>White>Lavender|
|12-Jan-20|Delaware Water Gap	    |[Mt Minsi via AT](https://www.alltrails.com/explore/recording/mount-minsi-via-appalachian-trail--1464)|
|15-Jan-20|Wissahickon	          |Kitchens Lane>White>Orange|
|19-Jan-20|	Hopewell FurnaceNHS/French Creek State Park	|[Lenape Trail to Mill Creek Trail Loop](https://www.alltrails.com/explore/recording/lenape-trail-to-mill-creek-trail-loop--69)|
|26-Jan-20|	Hickory Run SP	      |[Shades of Death](https://www.alltrails.com/explore/recording/shades-of-death-trail--588)|

```{r}

```

